---
title: "README"
output: html_notebook
---

## Labels for rivers in the ggplot2 framework

ggriverlab aims to introduce labels that follow lines to creat nice maps with ggplot2.
Maybe I should learn how to use GIS dedicated softwares, but it is more to implement this function in R.

## First step: positioning labels

Before having functional labels and defining nice default parameters that give nice maps, I need to implement and test the basic postiioning of labels along a path.



### TO DO LIST

- $\checkmark$ make it work with point: place points along the path in place of letters;
- $\checkmark$ include in geom;
- $\Box$ make it work with entire labels as an option;
- $\checkmark$ make it work with letters;


### TO DO if the rest is done and clean

- $\Box$ make river specific geom (size~order);
- $\Box$ make interactive tool to test the parameters; 
- $\Box$ find good default parameters;
- $\Box$ scale against text size or plot size ?;


## Demo

```{r gulk}
library(ggriverlab)
library(riverdist)
library(ggplot2)

river <- as.data.frame(Gulk$lines[4])
colnames(river) <- c("x", "y")

ggplot(river, aes(x,y)) + geom_path() + coord_fixed()
ggplot(river, aes(x,y)) + geom_path() + coord_fixed() + geom_river_label(aes(label = "Gulk", offset = 14000, dist = 1500, vpos = 2000, win = 3000))

# the full fiver

branches <- 1:14
branch_list <- lapply(branches, function(b, Gulk){
  river <- as.data.frame(Gulk$lines[b])
  colnames(river) <- c("x", "y")
  river$branch <- b
  return(river)
}, Gulk)
full_river<- do.call(rbind, branch_list)

ggplot(full_river, aes(x,y, group = branch, colour = branch)) + geom_path() + coord_fixed() + geom_river_label(aes(label = "Gulk", offset = 6000, dist = 2000, vpos = 3000, win = 3000))


```
```{r animate}
# install.packages('devtools')
# devtools::install_github('thomasp85/gganimate')
library(gganimate)

# generate data for the animation
offsets <- seq(2000, 21000, length.out = 10)
list_data <- lapply(offsets, function(os, river){
  river$off <- os
  return(river)
}, river)
data_offset <- do.call(rbind, list_data)

anim <- ggplot(data_offset, aes(x,y)) + geom_path() + coord_fixed() + geom_river_label(aes(label = "Gulk", offset = off, dist = 1500, vpos = 1500, win = 4000))+
  transition_states(off, 1, 3)
```
